Usability of Mobile Map Applications

### 2014-09-25 usability-study/usability-study.tex
add conclusion

\end{multicols}
\clearpage
\begin{multicols}{2}
[
Though usability metrics are extremely important in assessing a system, it is also important to heuristically evaluate systems in order to explore \textit{why} they performed the way they do.
My heuristic evaluations of the mobile map applications will be based on the guidelines documents that correspond to the applications.
\subsection{Apple Maps}
]
\par
\noindent
\includegraphics[width=.49\textwidth]{apple-maps.png}
The icons of the Google Maps mobile application comply with the Google Design Guidelines\cite{Google}: simple, modern, geometric in execution, and with rounded corners. Be that as it may, Google Maps completely fails to use any standard iOS icons:
\par
\noindent
\includegraphics[width=.45\textwidth]{ios-bar-icons.png}
\par
\noindent
Though it is not required to use these provided iOS icons, the iOS HIG (Human Interface Guidelines) state that it is ``a good idea to use the built-in icons as much as possible because users already know what they mean".\cite{Apple} Balancing consistency in platform with consistency of brand is a challenge, but there is a possibility that adhering more to the iOS HIG could improve usability of Google Maps. There was a higher percent of errors in clicking \underline{wrong icons} in the Google Maps application as there was in the Apple Maps application.

\end{multicols}
\clearpage
\section{Conclusion}
Usability stuff goes here. blah blah blah
\clearpage
\begin{thebibliography}{100} % 100 is a random guess of the total number of 
%references
\bibitem{Nielsen} Nielsen, Jakob, \emph{Usability Engineering}, Boston: Academic, 1993.
\bibitem{Mossberg} Mossberg, Walt., ``The iPhone Takes to the Big Screen," \emph{The Wall Street Journal}, September 2012.
\bibitem{ComScore}``Analytics for a Digital World - ComScore, Inc." \emph{ComScore, Inc}, 2012.
\bibitem{Google} \emph{Material Design}, www.google.com/design/spec/material-design.
\bibitem{Apple} \emph{iOS Human Interface Guidelines}, https://developer.apple.com/
\end{thebibliography}
%%%%%%%%%%%%% end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\end{multicols}
\clearpage
\begin{multicols}{2}
[
Though usability metrics are extremely important in assessing a system, it is also important to heuristically evaluate systems in order to explore \textit{why} they performed the way they do.
My heuristic evaluations of the mobile map applications will be based on the guidelines documents that correspond to the applications.
\subsection{Apple Maps}
]
\par
\noindent
\includegraphics[width=.49\textwidth]{apple-maps.png}
One idea that is emphasized in the \textit{iOS Human Interface Guidelines} is to always "defer to content".\cite[Apple] One way in which the guidelines recommend doing this is by taking advantage of the whole screen, which the Apple Maps mobile app seems to be doing. The UI helps people understand and interact with the content, but never competes with it. Reconsider visual indicators of physicality and realism. Bezels, gradients, and drop shadows sometimes lead to heavier UI elements that can overpower or compete with the content. Instead, focus on the content and let the UI play a supporting role.

\end{multicols}
\clearpage
\section{Conclusion}
The usability metrics of the Google Maps mobile application outranked those of the Apple Maps application in almost every way. Though there are some problems with the UI consistency, it does not seem to bother the users (refer back to satisfaction). Still, using non-standard icons or processes isn't without drawbacks. It's loud. It's authorial voice. It's greater cognitive load for users. Anything inconsistent, first or third party is. On an integrated platform like iOS, integrating with the platform offers a lot of benefits, especially when it comes to user experience.

If you use Google apps, either a lot or a little, does the lack of iOS-style buttons make any difference to you?

must recognize that there are limitations to our studies-- didn't test all five metrics; less data for Apple maps; Apple maps is newer; etc.
Judgment call -- google maps with data that we have now.
\clearpage
\begin{thebibliography}{100} % 100 is a random guess of the total number of 
%references
\bibitem{Nielsen} Nielsen, Jakob, \emph{Usability Engineering}, Boston: Academic, 1993.
\bibitem{Mossberg} Mossberg, Walt., ``The iPhone Takes to the Big Screen," \emph{The Wall Street Journal}, September 2012.
\bibitem{ComScore}``Analytics for a Digital World - ComScore, Inc." \emph{ComScore, Inc}, 2012.
\bibitem{Google} \emph{Material Design}, www.google.com/design/spec/material-design.
\bibitem{Apple} \emph{iOS Human Interface Guidelines}, https://developer.apple.com/
\end{thebibliography}
%%%%%%%%%%%%% end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
